Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-15 article.tex
EOD

We will reject
the null hypothesis that MHC-I has the same percentage of epitopes 
overlapping with TMHs in Homo sapiens compared to each pathogen when 
the KS statistic $D_{n,m}$ follows the relationship as shown in 
equation \ref{eq:ks}, for a significance level $\alpha = 0.05$
and $n = m = 13$ HLA haplotypes.

@@

\richel{Check against stupidity}
For MHC-II, we do the same analysis as MHC-I, except for
MHC-II haplotypes. We picked the top 21 MHC-II alleles that are most abundant 
in the current human population \richel{reference here}
%\frans{
%  Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. 
%  Misschien moeten we even de coverage erbij melden. 
%  Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
%}.
We chose to use 21 alleles to have a similar number of alleles as is done
for MHC-I.
Same as \cite{bianchi2017}, we defined the 5\% of polypeptides 
with the lowest IC50 values as binders. We then counted the percentage
of binders that have one or more amino acids that are part of a TMH.

@@

We thanks to Geert van den Bogaart for his wisdom.

@@

>>>>

We will reject
the null hypothesis that MHC-I has the same percentage of epitopes 
overlapping with TMHs in Homo sapiens compared to each pathogen when 
the KS statistic $D_{n,m}$ follows the relationship as shown in 
equation \ref{eq:ks}, for a significance level $\alpha = 0.05$
and $n = m$ equals the number of HLA haplotypes.

@@

\richel{Check against stupidity}
For MHC-II, we do the same analysis as MHC-I, except for
MHC-II haplotypes. We picked the top 21 MHC-II alleles that are most abundant 
in the current human population (\cite{greenbaum2011functional}).
%\frans{
%  Neem aan dat dit die ref is naar dat stukje van most common haplotype in human population. 
%  Misschien moeten we even de coverage erbij melden. 
%  Greenbaum, Jason, et al. "Functional classification of class II human leukocyte antigen (HLA) molecules reveals seven different supertypes and a surprising degree of repertoire sharing across supertypes." Immunogenetics 63.6 (2011): 325-335.
%}.
We chose to use 21 alleles to have a similar number of alleles as is done
for MHC-I.
Same as \cite{bianchi2017}, we defined the 5\% of polypeptides 
with the lowest IC50 values as binders. We then counted the percentage
of binders that have one or more amino acids that are part of a TMH.

@@

We thank the Center for Information Technology of the University 
of Groningen for its support and for providing access to the Peregrine 
high performance computing cluster.

@@

\begin{table}
  \input{mhc2_haplotypes.latex}
  \caption{
    Percentage of MHC-II haplotypes, from \cite{greenbaum2011functional}
  }
  \label{table:bbbq_2_percentages}
\end{table}
